quollr: An R Package for Visualizing 2-D Models from Non-linear Dimension Reductions in High Dimensional Space

### 2025-05-15 paper-quollr.Rmd
Started adding the acknowlegment section

```{r load-libraries}
library(quollr)
library(tibble)
library(knitr)
library(kableExtra)
library(ggplot2)
library(dplyr)
library(patchwork)
library(readr)
library(tools)

@@

## Package dependencies

Understanding the dependencies of the `quollr` package is essential for smooth operation and error prevention. The following dependencies refer to the other R packages that `quollr` relies on to execute its functions effectively.

```{r}
package_dependencies("quollr")
```

@@

This article is created using \CRANpkg{knitr} [@knitr] and \CRANpkg{rmarkdown} [@rmarkdown] in R with the `rjtools::rjournal_article` template. The source code for reproducing this paper can be found at: <https://github.com/JayaniLakshika/paper-quollr>.

>>>>

```{r load-libraries}
library(quollr)
library(tibble)
library(knitr)
library(kableExtra)
library(ggplot2)
library(dplyr)
library(patchwork)
library(readr)
#library(tools)

@@

@@

This article is created using \CRANpkg{knitr} [@knitr] and \CRANpkg{rmarkdown} [@rmarkdown] in R with the `rjtools::rjournal_article` template. These `R` packages were used for this work: `cli` [@gabor2025], `dplyr`, `ggplot2`, `interp` (>= 1.1-6), `langevitour`, `proxy`, `stats`, `tibble`, `tidyselect`, `crosstalk`, `plotly`, `kableExtra`, `patchwork`, and `readr`.

The source code for reproducing this paper can be found at: <https://github.com/JayaniLakshika/paper-quollr>.

### 2025-05-15 paper-quollr.tex
Started adding the acknowlegment section

\subsection{Package dependencies}\label{package-dependencies}

Understanding the dependencies of the \texttt{quollr} package is essential for smooth operation and error prevention. The following dependencies refer to the other R packages that \texttt{quollr} relies on to execute its functions effectively.

\begin{verbatim}
#> $quollr
#>  [1] "dplyr"       "ggplot2"     "grid"        "interp"      "langevitour"
#>  [6] "proxy"       "rlang"       "rsample"     "stats"       "tibble"     
#> [11] "tidyselect"
\end{verbatim}

@@

@@

\includegraphics[width=1\linewidth]{paper-quollr_files/figure-latex/unnamed-chunk-25-1}

@@

This article is created using \CRANpkg{knitr} \citep{knitr} and \CRANpkg{rmarkdown} \citep{rmarkdown} in R with the \texttt{rjtools::rjournal\_article} template. The source code for reproducing this paper can be found at: \url{https://github.com/JayaniLakshika/paper-quollr}.

>>>>

@@

\includegraphics[width=1\linewidth]{paper-quollr_files/figure-latex/unnamed-chunk-21-1}

@@

@@

This article is created using \CRANpkg{knitr} \citep{knitr} and \CRANpkg{rmarkdown} \citep{rmarkdown} in R with the \texttt{rjtools::rjournal\_article} template. These \texttt{R} packages were used for this work: \texttt{cli} \citep{gabor2025}, \texttt{dplyr}, \texttt{ggplot2}, \texttt{interp} (\textgreater= 1.1-6), \texttt{langevitour}, \texttt{proxy}, \texttt{stats}, \texttt{tibble}, \texttt{tidyselect}, \texttt{crosstalk}, \texttt{plotly}, \texttt{kableExtra}, \texttt{patchwork}, and \texttt{readr}.

The source code for reproducing this paper can be found at: \url{https://github.com/JayaniLakshika/paper-quollr}.
